FITS format for planetary surfaces: definitions, applications and best practices.

### 2018-05-12 ess_marmo.tex
Typo again..
Update on Overleaf.

We are aware that FITS is today subject of questioning in astronomical applications
\citep{THOMAS2015133}.
We are not convinced that one format can solve all the issues faced from long-term
archiving to on-line streaming.
Planetary science research community has used a large variety of format customizing
specific software.
We want to stress here that using FITS could be an efficient compromise, reducing custom
data format conversions during the processing chain and
allowing easy conversion for final products following the needed application.

>>>>

We understand that some believe FITS has grown too old for newer astronomical
applications \citep{THOMAS2015133}. We are also not convinced that one format
can solve all the issues faced from long-term archiving to on-line streaming.
But we want to stress that using FITS can be an efficient compromise.
FITS can become the format that allows the astronomy and the  planetary science 
research communities to more easily share data across domains, allowing for
reduced data format conversions during processing and easy conversion for final
archival products.
